%% LaTex template for a monographic dissertation
%% at the Faculty of Medicine at Heinrich Heine University Düsseldorf

%% author: Christian Olaf Häusler
%% date: January 2022
%% license:
%% Creative Commons Attribution 4.0 International Public License
%% https://creativecommons.org/licenses/by/4.0/

%% This template was created to meet the requirements as provided by:
%% ENG-PhD_Ordnung_vom_05.03.2018.pdf
%% DE-PhD_Ordnung_vom_05.03.2018.pdf
%% 2020-06-19_GZ-Guidelines_for_preparation_of_Dissertations_-_Monograph.pdf
%% 2021-04-01_GZ-Leitfaden_zur_Erstellung_von_klassischen_Dissertationen.pdf


% font size 11-12pt
\documentclass[english,12pt]{report}
\usepackage[utf8]{inputenc}

% use ä, ü, ...
\usepackage[T1]{fontenc}

% use a common font like Times New Roman or Arial:
% keep LaTex' standard ("Computer Modern")

% margins of the pages;
% left: 30-35mm (due to binding)
% right, top, bottom: 20-25mm
\usepackage[
    a4paper,
    left=30mm,
    right=20mm,
    top=20mm,
    bottom=20mm
]
{geometry}


% manage header, footers, and page numbers
\usepackage{fancyhdr}

% add to dos as comments
\usepackage{todonotes}

% manage spacing between lines
\usepackage{setspace}

% format the chapters' header
\usepackage{titlesec}
\titleformat{\chapter}[hang]{\bf\huge}{\thechapter}{2pc}{}
% other way without showing the number before the chapter title:
%\titleformat{\chapter}[display]{\normalfont\bfseries}{}{0pt}{\Huge}


% citation
% numerical citations:
%\usepackage[numbers]{natbib}
% superscript citations:
%\usepackage[super]{natbib}
% author-year citations:
% \usepackage[round]{natbib}
% APA-style citing and bibiliography
\usepackage[natbibapa]{apacite}

% make the bibliography appear in the table of contents
\usepackage[nottoc,numbib]{tocbibind}

% units: provided as a bundle with the nicefrac package for typing fractions.
% Units uses nicefrac in typesetting physical units in a standard-looking way.
\usepackage{units}

% how to handle links in the PDF
\usepackage[
    colorlinks=true,
    citecolor=black,
    urlcolor=black,
    linkcolor=black
]{hyperref}




\begin{document}
% set pagestyle to 'no header' and 'page number at bottom in the middle'
\pagestyle{plain}
% don't show page number (for now)
\pagenumbering{gobble}
% set spacing between lines to 1.5
\begin{spacing}{1.5}




% create the title page
\begin{titlepage}
\begin{center}

From the Institute Institute of Neuroscience and Medicine,\\
Brain \& Behaviour (INM-7),\\
at Research Centre Jülich, Jülich, Germany

\vfill

\textbf{{\large Evaluating common high-dimensional models of cortical
representational spaces for improving the power of neuroimaging-based
clinical diagnostics}}

maybe add subtitle

\vfill

{\large Dissertation}

\vfill

to obtain the academic title of Doctor of Philosophy (PhD) in Medical Sciences\\
from the Faculty of Medicine at Heinrich Heine University Düsseldorf

\vfill

submitted by\\
\textbf{Christian~Olaf~Häusler}\\
(2022)

\end{center}
\end{titlepage}




%\chapter*{Examiner Details}
\newpage
%pagebreak[4]

\todo[inline]{This page 2 will not be included in the examination copies,
    but will only be inserted in the copies for publication after the review
    process and the oral examination.}

\todo[inline]{You will be notified of the exact text for page 2 once print
    approval is granted.}

\vfill
\noindent As an inaugural dissertation printed by permission of the\\
Faculty of Medicine at Heinrich Heine University Düsseldorf

\vspace*{\fill}
\noindent signed:\\
dean:\\
examiner: Name A\\
co-examiner: Name B



%\chapter*{Dedication}
\newpage
%pagebreak[4]

\begin{center}
\null\vspace{\stretch{1}}
    \textit{pectus amico, cuspis hosti}
\vspace{\stretch{2}}\null
\end{center}




%\chapter*{List of Publications}
\newpage
%pagebreak[4]

\todo[inline]{Own publications are listed here. Submitted manuscripts or
    manuscripts under revision are not listed here. These will be
    listed in the “Application for authorization to the doctorate”
    (Zulassungsantrag)}

\todo[inline]{Please note that you must include a reference for all
    information you take from your own publications. The publications mentioned
    on page 4 must therefore also be listed in the bibliography. Direct
    quotations must be marked with quotation marks}

\vspace*{\fill}

\noindent \textbf{Parts of this work have been published:}\\

\todo[inline]{just testing the bibliography}

% just testing the bibliography
\citep{haeusler2021speechanno},
\citep{halchenko2021datalad},
\citep{haeusler2021ppadata}
\chapter*{Zusammenfassung}
% show page number
\pagenumbering{Roman}
\setcounter{page}{1}

\todo[inline]{The German and English summary should be exactly one page long
each. The summary represents a coherent text. Please do not use subheadings. The
summary should include the following content in a shortened form:\\
the scientific background and current state of research\\
research question and objectives\\
methodology\\
results\\
discussion and conclusions.
}

\todo[inline]{The summary is needed twice:\\
    a) Bound into your dissertation.\\
    b) As a pdf-document, submitted together with the application for
    admission to doctoral examination proceedings.
}

% wissenschaftlicher Hintergrund
lore ipsum
% aktuelle5 Forschungsstand

% Fragestellung und Ziele

% Methodik

% Ergebnisse

% Diskussion

% Schlussfolgerungen




\chapter*{Summary}

% scientific background
lore ipsum
% current state of research

% research question and objectives

% methodology

% results

% discussion

% conclusions

% lore ipsum




\chapter*{Abbreviations}

%
\todo[inline]{The list of abbreviations contains and explains all abbreviations
used in the thesis (except for common linguistic abbreviations as defined in the
dictionary, e.g. Duden, Merriam-Webster). In the case of physical or chemical
quantities, it is also necessary to specify the unit. An alphabetical order is
useful, a subdivision (e.g. SI units, own abbreviations) is possible. For
example, you can format the page in two columns, the abbreviations in bold and
the corresponding explanations in non-bold.}




\tableofcontents

\todo[inline]{The entire table of contents should not be longer than 2 pages.}
%
\todo[inline]{A chapter with only one subchapter is not allowed}




\listoftables

\todo[inline]{does not seem to be mandatory?}




\listoffigures

\todo[inline]{does not seem to be mandatory?}




\chapter{Introduction}
% formatting stuff
\pagenumbering{arabic}
\setcounter{page}{1}

% use an external file
\input{introduction}




\chapter{Material and Methods}

\todo[inline]{This chapter contains information on patients, examination
materials and methods, depending on the research project. With the help of this
chapter, readers must be able to understand and, if necessary, repeat all
examinations and experiments.}

\todo[inline]{Information on Patients: The statistical information to be
mentioned or described includes number of patients, gender distribution, and age
of patients (mean and median).}

\todo[inline]{Reference Number issued by Ethics Committee: When results from
clinical studies are part of the research project, the reference number assigned
by the Ethics Committee of Heinrich Heine University upon approval must be
stated in the chapter Material and Methods.}

\todo[inline]{Reference Number issued by LANUV or ZETT: For work comprising
results from animal testing, the file reference assigned by LANUV during the
approval procedure must be given in the chapter Materials and Methods, or, in
the case of organ removal, the file reference allocated by ZETT of Heinrich
Heine University. A proof of participation in the laboratory animal science
course must also be given, if applicable.}

\todo[inline]{Methods and Material: This chapter lists: Type and origin of the
material, hardware/equipment with type, manufacturer, location, a detailed
description of the methods used.}

\todo[inline]{Statistical Analysis A short and clear
description of the methods used for material processing, data processing and
statistical analysis.}




\chapter{Results}

\todo[inline]{This chapter contains a clear and concise presentation of your own
results with reference to the research question of the thesis. Results that do
not directly relate to the aim of the thesis should not be included here. Avoid
any interpretation or discussion of the findings in the results chapter. Cite
your own, already published data in the results chapter if you use them in your
work. Further literature citations do not belong in the results chapter.
%
Results of others may not be included in the results chapter. Refer to other
people's results either in the introduction or in the discussion. In order to
use data as a graph, illustration or table, you must obtain written permission
by the author.}




\chapter{Discussion}

% use an external file
\input{discussion}



%% References
% \bibliographystyle{unsrtnat}
\bibliographystyle{apacite}
\bibliography{references}

\todo[inline]{if APA-style is used, show all (i.e. more than 7) authors}



% Appendix
%\appendix

\chapter{Appendix}

\todo[inline]{The appendix contains:\\
a) any existing survey materials, e.g. questionnaires\\
b) detailed description of formulas and derivations\\
Please do not include signed documents (e.g. the vote of the Ethics Committee)}

\input{appendix}




\chapter*{Acknowledgments}
% don't show page number
\pagenumbering{gobble}
% text
I want to thank...
% family
Vadda; Gabriele; Nico, Anna, Antonia, Julius; Annelie, Johannes;
%
Niklas Lampe, Ken Waigel, Brahim Sokoli, Stefan Mysliwietz, Ilja Rabinovitch,
Ruwen Jeffe;
% colleagues
Adina Wagner, Alex and Laura Waite, Julia Mahns, Markus Thoma;
% Mitbewohner
Christian Fröhlich, Kyesam Jung, Binny Davis;
% landlord
Mr. Halking;
% job
Anika Völkel;
% eating
Trojan Pizzeria;
% bands
Heaven Shall Burn, Black Sun Empire, Hatebreed, The Ghost Inside, Emmure,
Babymetal, Lorna Shore ("...And I Return To Nothingness EP"!);
% bosses
Simon Eickhoff, Gerhard Jocham, foremost Michael Hanke
%


\chapter*{Declaration of authorship}
%
\todo[inline]{The affidavit (declaration of Authorship) is signed in the
``Application for authorization to the doctorate'' (Zulassungsantrag). According
to the PO, the affidavit is no longer inserted in the dissertation itself.}

\end{spacing}
\end{document}
